msb106_assignment

### 2024-01-18 msb106_assignment.qmd
rg3w
fjew

>>>>

```{r}
maindata <- maindata %>%
  group_by(geo, TIME_PERIOD) %>%
  mutate(arb.ledig.geo.mean = mean(arbeidsledig, na.rm = TRUE), huspris.geo.mean = mean(huspris, na.rm = TRUE), arb.vekst.geo.mena = mean(arbeidsvekst, na.rm = TRUE))

```{r}
maindata <- maindata %>%
  mutate(classification = case_when(
    arbeidsledig > arb.ledig.geo.mean & arbeidsvekst > arb.vekst.geo.mena & huspris > huspris.geo.mean ~ "1.høy arbeisledighet, høy arbeidsvekst, høy huspris",
    arbeidsledig > arb.ledig.geo.mean & arbeidsvekst > arb.vekst.geo.mena & huspris <= huspris.geo.mean ~ "2.høy arbeisledighet, høy arbeidsvekst, lav huspris",
    arbeidsledig > arb.ledig.geo.mean & arbeidsvekst <= arb.vekst.geo.mena & huspris > huspris.geo.mean ~ "3.høy arbeisledighet, lav arbeidsvekst, høy huspris",
    arbeidsledig > arb.ledig.geo.mean & arbeidsvekst <= arb.vekst.geo.mena & huspris <= huspris.geo.mean ~ "4.høy arbeisledighet, lav arbeidsvekst, lav huspris",
    arbeidsledig <= arb.ledig.geo.mean & arbeidsvekst > arb.vekst.geo.mena & huspris > huspris.geo.mean ~ "5.lav arbeisledighet, høy arbeidsvekst, høy huspris",
    arbeidsledig <= arb.ledig.geo.mean & arbeidsvekst > arb.vekst.geo.mena & huspris <= huspris.geo.mean ~ "6.lav arbeisledighet, høy arbeidsvekst, lav huspris",
    arbeidsledig <= arb.ledig.geo.mean & arbeidsvekst <= arb.vekst.geo.mena & huspris > huspris.geo.mean ~ "7.lav arbeisledighet, lav arbeidsvekst, høy huspris",
    arbeidsledig <= arb.ledig.geo.mean & arbeidsvekst <= arb.vekst.geo.mena & huspris <= huspris.geo.mean ~ "8. lav arbeisledighet, lav arbeidsvekst, lav huspris",
    TRUE ~ "unknown")
  )
```
